SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-06 scipy-1.0/ckdtree.tex
Update ckdtree.tex

In 2015, SciPy added the \texttt{sparse\_distance\_matrix} routine for generating approximate 
sparse distance matrices between \texttt{KDTree} objects by ignoring all distances that 
exceed a user-provided value. Also, this routine allows any Minkowski p-norm between 1 and 
infinity and it is not limited to the conventional L2 (Euclidean) norm. 
By default, the returned data structure is a dictionary of keys (DOK) based sparse matrix, 
which is very efficient for matrix construction. 
This hashing approach to sparse matrix assembly can be 7 times faster than constructing 
with compressed row format (CSR) \cite{10.1007/978-3-540-75755-9_107} and the C++ level 
sparse matrix construction releases the Python GIL for increased performance. 
Once the matrix is constructed, distance value retrieval has an amortized constant time 
complexity \cite{Cormen:2001:IA:580470}, and the DOK structure can be efficiently converted 
to a CSR, CSC or COO matrix to allow for speedy arithmetic operations.

>>>>

In 2015, SciPy added the \texttt{sparse\_distance\_matrix} routine for generating 
approximate sparse distance matrices between \texttt{KDTree} objects by ignoring 
all distances that exceed a user-provided value. Also, this routine it is not 
limited to the conventional L2 (Euclidean) norm but supports any Minkowski 
p-norm between 1 and infinity. By default, the returned data structure is a 
Dictionary Of Keys based sparse matrix (DOK), which is very efficient for matrix 
construction. This hashing approach to sparse matrix assembly can be 7 times 
faster than constructing with Compressed Sparse Row format (CSR) 
\cite{10.1007/978-3-540-75755-9_107} and the C++ level sparse matrix construction 
releases the Python GIL for increased performance. Once the matrix is constructed, 
distance value retrieval has an amortized constant time complexity 
\cite{Cormen:2001:IA:580470}, and the DOK structure can be efficiently converted 
to a CSR, Compressed Sparse Column (CSC) or COOrdinate (COO) matrix to allow for 
speedy arithmetic operations.
